\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{biolinum}
\usepackage{url}
\usepackage{hyperref}
\usepackage[top=10mm, bottom=15mm, left=15mm, right=15mm]{geometry}
\usepackage{parskip}
\usepackage{paralist}
\usepackage{microtype}
\usepackage{sectsty}
\usepackage{multicol}

\setlength{\columnsep}{8mm}
\setdefaultleftmargin{1.5em}{0em}{}{}{}{}
\allsectionsfont{\sffamily}
\hypersetup{hidelinks=true,colorlinks=true}

\begin{document}
\thispagestyle{empty}
\sffamily

{\bfseries\huge Jan Špaček}

\begin{multicols}{2}

I am a software engineer. I have worked on projects including:
\begin{compactitem}
  \item High-performance distributed systems
  \item Deep learning
  \item Embedded devices
  \item Network protocols
  \item Web apps
  \item Desktop apps
  \item Physically-based renderer
  \item Programming language
  \item Mobile app
\end{compactitem}

\section*{Work experience}

\textbf{Chiselstrike} (remote, 2022-present)
  \newline Participated in development of a custom JavaScript runtime
  environment based on Deno.
  \newline Various contributions across many projects.
  \newline Design and prototyping of an edge-first ORM library.
  \newline Rust, TypeScript, Deno, SQLite

\textbf{Ullmanna} (remote/Opava, 2020-present)
  \newline \textbf{Co-founder}, responsible for most of the software.
  \newline Software for a robotic weeding machine (agriculture).
  \newline State-of-art recognition of plants in real time with machine learning.
  \newline Novel algorithm for visual odometry with stereo vision.
  \newline Telemetry, remote update, data collection.
  \newline Tablet app for the end user.
  \newline Participated in electronics design and development.
  \newline Rust (async), C++, CUDA, Python, PyTorch, Android with Kotlin, KiCad, Buildroot

\textbf{Kiwi.com} (remote, 2020-2021)
  \newline Maintenance of legacy distributed search services (part of a team).
  \newline Introducing Rust into smaller services.
  \newline C++, Python, Rust (all async)

\textbf{Quantlane} (Prague, 2019)
  \newline Development and maintenance of a legacy trading system (part of a
  team).
  \newline Python with asyncio, RabbitMQ

\textbf{Corona Renderer} (remote, 2017–2019)
  \newline Integration of Corona Renderer into ARCHICAD.
  \newline Bachelor thesis supervised by Jaroslav Křivánek.
  \newline C++ for Windows, using ARCHICAD APIs and Corona API

\textbf{Kiwi.com} (remote, 2016, 2017)
  \newline Distributed in-memory database with low latency and high throughput
    for storing flight combinations.
  \newline Distributed engine for precomputing flight combinations (part of a
    team, major contribution).
  \newline Distributed system for bulk reading of flights from Cassandra.
  \newline C++, Python with asyncio, using Cassandra, Redis, PostgreSQL,
    docker

\textbf{Bileto} (remote, 2015)
  \newline Engine for real-time routing in public transport networks (part of a
  team).
  \newline C++, using Redis and PostgreSQL

\columnbreak

\textbf{Adash} (remote/Ostrava, 2014–2015)
  \newline An application to visualize measured vibrations of industrial
  machinery.
  \newline Design of efficient digital filters accelerated using advanced
  features of ARM processors.
  \newline C++, wxWidgets.


\section*{Selected projects}

\textbf{Makiko} (2022-present)
  \newline Asynchronous SSH client library for Rust.
  \newline Rust, Tokio

\textbf{SkyGAN} (2019–2020)
  \newline Generating high-resolution skydome images with deep generative
  adversarial networks (GAN).
  \newline Master thesis supervised by David Futschik and Alexander Wilkie.
  \newline Python with PyTorch

\textbf{Dancerank.cz} (2016–present)
  \newline A large database of dance sport results and competitions from several
  countries with analysis of results.
  \newline Predictions using a novel machine learning model.
  \newline Custom search engine in C++
  \newline Python with asyncio, using MongoDB and Redis

\textbf{dort} (2016–2017)
  \newline A physically based renderer heavily influenced by pbrt.
  \newline C++, Lua

\textbf{Spiral} (2015)
  \newline Implementation of a programming language: compiler, runtime support
  library with garbage collection, standard library.
  \newline C++, Rust, x86 assembler, Spiral.

\ldots{}and a large amount of smaller projects, a few of them are on my GitHub 
\href{https://github.com/honzasp}{@honzasp}.

\section*{Skills}

I am not limited to any particular language, platform or environment. I am most
experienced in Rust, C++ and Python, but I also wrote
{\small TypeScript/JavaScript, Kotlin,}
{\footnotesize C\#, Haskell, Ruby, Lua, Go,}
{\scriptsize Clojure, OCaml, Java, my own language Spiral, ...}

I have a master's degree in computer science from Matfyz (2015-2020).

Beside work, I danced Latin on a competition level (reached the highest national
class``A'' with my partner). I am also an avid reader in English and Czech.

\section*{Contacts}

Web: \url{https://honzasp.github.io}\newline
GitHub: \href{https://github.com/honzasp}{@honzasp}\newline
LinkedIn: \href{https://www.linkedin.com/in/honzasp}{Jan Špaček}\newline

\end{multicols}
\end{document}
